---
title: "dolores"
output: html_document
---
Load libraries
```{r}
library(dplyr)
library(magrittr)
```

Load Anne's DESeq results. These lists include all genes.  
Notes:  

 * I replace log2FoldChange with 0 for all genes with baseMean==0. These used to be marked NA but we want to include in permutations and note that they show no difference.
 * in code below, I redo FDR and adjusted pvalues. I think these were wrong?  

```{r}
teo<-read.table("~/Desktop/teo_anne.csv",header=T,sep=",") %>% mutate(padj=p.adjust(pvalue,method="fdr"))
maize<-read.table("~/Desktop/maize_anne.csv",header=T,sep=",") %>% mutate(padj=p.adjust(pvalue,method="fdr"))
anne<-merge(teo,maize,by.x="gene",by.y="gene",suffixes=c(".teo",".maize")) %>% mutate(log2FoldChange.maize=ifelse(is.na(log2FoldChange.maize),0,log2FoldChange.maize), log2FoldChange.teo=ifelse(is.na(log2FoldChange.teo),0,log2FoldChange.teo))
```

Load Zak Lemmon's allele specific expression results and combine with Anne's. We lose some genes -- down to ~25K.  
Notes:  

 * I add a pseudocount of 1 to Zak's leaf (for now) data to avoid 0 expression giving "Inf" values.  


```{r}
zak<-read.csv("~/Desktop/DE_analaysis.csv",header=T) %>% mutate(ParentMaize.Leaf=ifelse(ParentMaize.Leaf==0,1,ParentMaize.Leaf),ParentTeosinte.Leaf=ifelse(ParentTeosinte.Leaf==0,1,ParentTeosinte.Leaf))
zam<-merge(anne,zak,by.x="gene",by.y="Gene") 
```

How many teosinte DE genes? 

```{r}
length(filter(zam,zam$padj.teo<0.05)[,1])
```

How many of those are *not* DE in maize? 

```{r}
length(filter(zam,zam$padj.teo<=0.05,zam$padj.maize>0.05)[,1])
```

And how many are in the same direction in maize vs. teosinte (from Lemmon's data) as they are in modern vs. holocene (from our data)?

```{r}
length(filter(zam,zam$padj.teo<=0.05,zam$padj.maize>0.05,zam$log2FoldChange.teo*log2(zam$ParentMaize.Leaf/zam$ParentTeosinte.Leaf)>0)[,1])
```

Let's list those
```{r}
zam.candidates<-filter(zam,zam$padj.teo<=0.05,zam$padj.maize>0.05,zam$log2FoldChange.teo*log2(zam$ParentMaize.Leaf/zam$ParentTeosinte.Leaf)>0)
zam.candidates$gene
```

How many are also domestication genes. 

```{r}
length(filter(zam.candidates,Domestication==TRUE)[,1])
```

Let's list those too
```{r}
filter(zam.candidates,Domestication==TRUE)$gene
```

What percent of random samples of similar size have more domestication genes.

```{r}
sum(sapply(1:1000,function(x) sum(sample(zam$Domestication,47))>3))/1000
```

So we have 47 potential assimilation loci and 3 awesome candidates that also show selection.

Finally, because I redid adjusted p-values, here's the list of DE genes in teosinte:
```{r}
filter(zam,zam$padj.teo<=0.05)$gene
```

